Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-15 nips_2018.tex
shorter

We compare  with four baselines on  held-out tasks:
\\\noindent \textbf{Ours (no NN)}, which lesions the recognition model.
\\\noindent \textbf{RF/DC}, which holds the generative model $(\mathcal{D},\theta)$ fixed and learns
a recognition model only from samples from the fixed generative model.
This is equivalent to our algorithm with $\lambda = \infty$ (Sec.~\ref{grammarInductionSection})
and $\mathcal{L}_{\text{RM}} = \mathcal{L}_{\text{HM}}$ (Sec.~\ref{recognitionSection}).
We call this baseline RF/DC because
this setup is closest to how RobustFill~\cite{devlin2017robustfill} and DeepCoder~\cite{balog2016deepcoder} are trained.
We can not compare directly with these systems,
because they are engineered for one specific domain, and 
do not have publicly available code and datasets.
\\\noindent \textbf{PCFG}, which lesions the recognition model, learns $\theta$, and fixes $\mathcal{D}$.
This is equivalent to our algorithm with $q(x) = \theta$ and $\lambda = \infty$,
and is like learning the parameters of a PCFG while not learning any of the structure.
\\\noindent \textbf{Enum}, which does no learning and just enumerates a frontier.
This is equivalent to our first wake cycle.

For each domain,
we are interested both in how many tasks the
agent can solve and how quickly it can find those solutions.
For symbolic regression, we also care about the quality
of the solution, as measured by the likelihood model $\probability[x|p]$,
e.g. did the agent correctly explain a linear function
using two numbers, or did it introduce extraneous parameters?
Tbl.~\ref{baselineComparisons}
compares our model against these baselines.
Our full model consistently
improves on the baselines,
sometimes dramatically (string editing and symbolic regression).
The recognition model 
consistently increases the number of solved held-out tasks,
and lesioning it also slows down the convergence of the algorithm,
taking more wake/sleep cycles to reach a given number of tasks solved (Fig.~\ref{learningCurves}).
This supports the view of the recognition model as a way of accelerating the search over programs.

\begin{table}
%% This radically shrinks the table
\tabcolsep=4pt
\renewcommand{\arraystretch}{0.5}
\begin{tabular}{llllll}
  \toprule& Ours& \begin{tabular}{c}
    Ours\\(no NN)
    \end{tabular}& RF/DC & PCFG & Enum

@@

  \\\midrule\multicolumn{6}{c}{\emph{Symbolic Regression}}\\\midrule
  \% solved&   \textbf{98\% }&94\%&0.7\%&0\%&2\% \\
  Solve time&  2.7s& 2.8s  &3.6s&--&2.1s\\
  MDL (nats)&   9.3 &11.0&2.3&--&4.6

@@

  \\\midrule\multicolumn{6}{c}{\emph{List functions}}\\\midrule
  \% solved&\textbf{86\%} &84\% &60\%&74\%&70\%\\
  Solve time&  0.8s&0.7s&1.0s&1.0s&1.1s
  \\\bottomrule
  \end{tabular}
\caption{\% solved w/ 5 sec timeout. Solve time: averaged over solved
  tasks.  RF/DC: trained like RobustFill/DeepCoder.  PCFG: model w/o
  structure learning.  Enum: model w/o any learning.  MDL:
  $-\expect\left[\probability[x|p] \right]$. For domains other than
  symbolic regression MDL is 0 nats. For symbolic regression MDL is a
  proxy for \# of continuous parameters.}\vspace{-0.5cm}\label{baselineComparisons} \end{table}

>>>>

We compare  with four baselines on  held-out tasks:
\\\noindent \textbf{Ours (no NN)}, which lesions the recognition model.
\\\noindent \textbf{RF/DC}, which holds the generative model $(\mathcal{D},\theta)$ fixed and learns
a recognition model only from samples from the fixed generative model.
This is equivalent to our algorithm with $\lambda = \infty$ (Sec.~\ref{grammarInductionSection})
and $\mathcal{L}_{\text{RM}} = \mathcal{L}_{\text{HM}}$ (Sec.~\ref{recognitionSection}).
We call this baseline RF/DC because
this setup is closest to how RobustFill~\cite{devlin2017robustfill} and DeepCoder~\cite{balog2016deepcoder} are trained.
We can not compare directly with these systems,
because they are engineered for one specific domain, and 
do not have publicly available code and datasets.
\\\noindent \textbf{PCFG}, which lesions the recognition model, learns $\theta$, and fixes $\mathcal{D}$.
This is equivalent to \system with $q(x) = \theta$ and $\lambda = \infty$,
and is like learning the parameters of a PCFG while not learning its structure.
\\\noindent \textbf{Enum}, which enumerates a frontier without any learning -- equivalently, our first exploration cycle.

For each domain,
we are interested both in how many tasks the
agent can solve and how quickly it can find those solutions.
%% For symbolic regression, we also care about the quality
%% of the solution, as measured by the likelihood model $\probability[x|p]$,
%% e.g. did the agent correctly explain a linear function
%% using two numbers, or did it introduce extraneous parameters?
Tbl.~\ref{baselineComparisons}
compares our model against these baselines.
Our full model consistently
improves on the baselines,
sometimes dramatically (string editing and symbolic regression).
The recognition model 
consistently increases the number of solved held-out tasks,
and lesioning it also slows down the convergence of the algorithm,
taking more iterations to reach a given number of tasks solved (Fig.~\ref{learningCurves}).
This supports a view of the recognition model as a way of amortizing the cost of searching for programs.

\begin{wraptable}{r}{0.6\textwidth}
%% This radically shrinks the table
\tabcolsep=4pt
\renewcommand{\arraystretch}{0.5}
\begin{tabular}{llllll}
  \toprule& Ours& \begin{tabular}{c}
    Ours\\(no NN)
    \end{tabular}& RF/DC & PCFG & Enum

@@

  \\\midrule\multicolumn{6}{c}{\emph{Symbolic Regression}}\\\midrule
  \% solved&   \textbf{98\% }&94\%&0.7\%&0\%&2\% \\
  Solve time&  2.7s& 2.8s  &3.6s&--&2.1s\\
  %% MDL (nats)&   9.3 &11.0&2.3&--&4.6

@@

  \\\midrule\multicolumn{6}{c}{\emph{List functions}}\\\midrule
  \% solved&\textbf{86\%} &84\% &60\%&74\%&70\%\\
  Solve time&  0.8s&0.7s&1.0s&1.0s&1.1s
  \\\bottomrule
  \end{tabular}
\caption{\% solved w/ 5 sec timeout. Solve time: averaged over solved
  tasks.  RF/DC: trained like RobustFill/DeepCoder.  PCFG: model w/o
  structure learning.  Enum: model w/o any learning.  %% MDL:
  %% $-\expect\left[\probability[x|p] \right]$. For domains other than
  %% symbolic regression MDL is 0 nats.
  %% For symbolic regression MDL is a
  %% proxy for \# of continuous parameters.
}\vspace{-0.5cm}\label{baselineComparisons} \end{wraptable}
